Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 reviews/response.tex

\begin{document}
 \maketitle

 \section{Summary of the revision}

 We sincerely thank the managing Editor and the five anonymous referees for their very helpful and constructive suggestions.  We really 
 appreciate the reviewers' time, effort, and thoughtful suggestions, which stimulated us to substantially revise and improve the manuscript.
 We begin with a high-level description of our edits and in the following section we respond to some of the more major 
 specific points raised by the reviewers.  We do not list a large number of smaller edits made to the manuscript.
%  \item {\bf (Brief description)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
%  which amount to a total of 125 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
%  as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
%  in the context of the existing literature and some auxiliary facts from probability and extreme value theory.  For convenience of the reader, we 
%  have added statements of Slepyan's Lemma and the Sudakov-Fernique inequality (without proofs).
%  
%   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive
%   iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
%   in the literature.  The chapter contains also some new results on the (sub)optimality of some popular statistics, which appear to have been 
%   overlooked in the literature (Theorem 3.1).  One main idea  behind the exposition is to systematically present the different types of phase transition 
%   results as a function of the chosen statistical risk.  
%   
%   Chapters 4 through 7 contain the core of our original contributions.  
%   
%   Chapter 4 establishes phase-transitions results for the exact support recovery problem in the additive error model.  The main themes of this 
%   chapter are {\em error--dependence} and {\em concentration of maxima}. We establish that the notion of uniform relative stability -- 
%   a type of concentration of maxima phenomenon -- is key to characterizing the phase-transition in exact support recovery for the general class 
%   of thresholding estimators. 
%   
%   Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
%   Criteria for the latter are established and certain theoretical results indicate that {\em likelihood thresholding} (as opposed to data thresholding)
%   is in general optimal, when the thresholding estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., 
%   for log-concave error densities, our results entail 
%   a universal statistical limit in the exact support recovery problem, valid for all estimators (Theorem 5.3).   On the other hand, for the general class of
%   thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
%   structure that satisfies the mild uniform relative stability condition (Corollary 5.3).
%   
%   Chapter 6 is nearly unchanged. It is more probabilistic in nature and it provides a complete characterization of the uniform relatively stable (URS) Gaussian 
%   triangular arrays.  This URS condition is the key property used to establish the lower bound on exact support recovery under dependence in Chapter 4. 
%   These probabilistic results as well as their methods of proof may be of independent interest and are presented in a way that should be 
%   accessible to a wider audience of graduate students in statistics. 
%   
%   Chapter 7 focuses on an application to genome-wide association studies (GWAS) in statistical genetics.  It is shown that all phase-transition results in the 
%    additive error models of Chapter 3, have their close counterparts for the chi-square models arising naturally in GWAS. To connect these
%    asymptotic results to the practical notions in statistical genetics, we establish the connection between the odds-ratio (effect size) in multinomial 
%    $2\times 2$ models
%    and the signal-size parameter of the corresponding chi-square association test.  This allows us to quantify the statistical power and
%     optimal design questions in a unified manner as well as ultimately explain the role of phase-transitions in the fundamental statistical limits of GWAS.
%

  \item {\bf (Organization)} 
  The manuscript has been revised substantially to include a brief introductory chapter and 6 substantive chapters, which amount to a total of 125 pages.
  As with the original submission, Chapter 2 reviews the statistical risks, estimation and testing procedures, as well as probability models for the errors used in the rest of the manuscript.

  After very careful deliberation, we decided to keep most of the content in Chapter 3, which provides a panorama of the phase-transition results in the signal detection and support estimation problems for the additive iid Gaussian error model.
  There were some mixed opinions from the reviewers regarding the inclusion of a chapter that paints the landscape in broad strokes and provides references to the state-of-the-art of the literature, at the expense of delaying entirely original contributions.
  We think that providing an accessible account of the subject of high-dimensional multiple testing would benefit readers who are not already experts in the area, and might just narrowly outweigh the additional patience required on the part of experts before we get to the more exciting material.
  Details and explanations of the changes we made can be found in the reponse to Reviewer 2 below.

  To better balance the exposition, we reorganized Chapter 4 of the previous version of the draft into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'',  and Ch.\ 5 ``Bayes and Minimax Optimality''). 
  This change, in addition to making all chapters more manageable and of about equal lengths, exposes more clearly our contributions. 
  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and the more applied Chapter 7 are original contributions to the literature.

  Following the suggestion of Reviewer 2 ({\bf R2}),  we have placed most proofs in the text after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of the SpringerBriefs series, we no longer include ``Exercises'' sections.

  \item {\bf (Typos, grammar, and style)}  Prompted by criticism of a referee ({\bf R2}), we have revised the language of the manuscript. 
  We have corrected a number of typos and missing articles.   
  There have been re-writes throughout the manuscript in order to make the style more consistent.  
  In trying to make the text more accessible, we re-formatted the statements of most theorems to make them more modular.

 \item {\bf (Length and online supplement)} We have shortened the manuscript to just under 125 pages. The Appendix appearing after the 
 References is meant to become an online supplement when the manuscript becomes ready for publication.  The appendix contains some proofs of phase-transition results stated in Ch.\ 7, which are similar to ones appearing in Ch.\ 3.% as well as some phase transition results for lighter and/or
 %heavier tailed models than the AGG class.  
 Thus, even without the online supplement, not much is lost by not including the Appendix in the printed version.

@@

 \end{itemize}

 \section{Responses to specific points raised by the reviewers}

 \subsection{Reviewer 1 (R1)}

 We are grateful for the positive comments and important feedbacks from the reviewer.

@@

  \item {\em  The manuscript contains sufficiently new topics especially the application in Chapter 4 to dependent data. This is an important topic and has not received as much attention in the high-dimensional literature as it should.

  \centerline{$\cdots$}

  The manuscript is generally well-written and the issues/problems are clearly laid out. On the other hand, the writing may be a bit overly concise for which a supplement would be needed in a topics course. But the authors seem to be aware of this aspect.}

  Thank you.  Stimulated by your feedback, we have attempted to provide more details and background where necessary.  In the interest of space and to 
  conform to the format of the SpringerBriefs series, we had to relegate some of the proofs in Chapter 7 (new labeling) to an online supplement.  This still 
  allowed us to treat carefully the important application to GWAS.  We believe we have also improved the treatment of the exact support recovery topic under 
  dependence.  As indicated above, we divided the phase-transitions results (under dependence) and the Bayes and minimax optimality results into 
  two separate chapters (Ch.\ 4 and 5, now).   We have added some more insights to the statements in Ch.\ 3 and Ch.\ 7, as well as some more 
  background material in Ch.\ 2.  
  These changes, in addition to making the more advanced material accessible, should improve the balance between the chapters and make them read better independently, thus making the text better suited for a special topics course.

@@

  \subsection{Reviewer 2 (R2)}

  We really appreciate the reviewer's feedback and suggestions.   We have taken all of them into account while revising the manuscript.

   \begin{itemize}

     \item {\em The book project grew out of the thesis of Z. Gao and some related articles. The main idea is about concentration of maxima in the sense of a law of large numbers (which is a rather rough result in this context; it could be supplemented by finer results on large deviations of maxima, as used in the context of a.s.\ convergence of maxima; e.g. the cited results of Barndorff; Resnick, Tomkins. BTW the best results on a.s. stability of maxima are due to Klass) and to exploit this fact for various applications.
}

@@

     \item {\em The manuscript is well written in general and the English is basically ok. There are some problems with articles... In my opinion, the authors exaggerate their explanations in the first chapters. There are repetitions of text and references.

     \centerline{$\cdots$}

     It is not clear whether the authors aim at a textbook or a monograph: some chapters contain exercises, others do not. For briefs the text is already too long in the present state. The authors could easily extend the manuscript to more than 200 pages, for example by extending the exercises and reorganizing the text.}

     We have thoroughly revised the exposition and fixed hopefully all typos and grammatical errors.  We have also streamlined the exposition 
     and tried to ground it.

     As indicated above, we have shortened the manuscript, eliminated the exercises, and cast it into the format of a SpringerBriefs monograph.  We 
     appreciate the reviewer's suggestions on extending the manuscript, but we felt that the work is not mature enough to ne expanded into a longer textbook.
     In trying to balance the chapter lengths and content, we believe now the manuscript is more appropriate for an auxiliary text in a special topics graduate course on high-dimensional statistics.

@@

     \item {\em For my taste, the authors take too long to come to the point. An example is Chapter 3. The authors cite dozens of sources before they come to their own results. I think this is the wrong approach. The main line of the manuscript should be to present own results. The results of others and their relation to those in the book can be discussed anywhere else, e.g. in comments after the results, or at the end of a section or chapter. It honors the authors that they want to quote correctly and give merit to previous work, but this approach disturbs the flow.}

     We really appreciate the feedback, which prompted us to thoroughly revise the presentation.

     The main goal of Chapters 2 and 3 is to shed light on the relationships between typical high-dimensional problems and their respective statistical limits. 
     In particular, Ch.\ 3 reviews the existing literature, and provide a unified treatment of the phase transitions under different loss functions.
%     To the best of our knowledge, such a unified treatment has not been available before.

     The inclusion of material surrounding Theorem 3.1 seems to be of concern.
     Indeed, Theorem 3.1 summarizes some known results in the signal detection problem, which may be familiar to experts in the field.
     On the other hand, Theorem 3.1 also presents some new, previously overlooked results on the sub-optimality of certain popular statistics. 
     These results are not the most exciting advances in either methodology or theory (and unfortunately will likely not be found in a journal publication because of their perceived lack of novelty). Nevertheless, they are natural and practically important questions that needed answers.
     In addition to these incremental contributions, we think that there is some value in collecting a range of related problems and results in one place. This inclusion of a bird's-eye view, however cursory,  would make the text more suitable for an introduction to a wider audience. 
     To emphasize this role, we changed the title of this chapter to ``A panorama of phase transitions''.

%     The results in Chapter 3 are also closely connected to the phase-transition results in Chapter 7 on GWAS. 
%     This exposition allowed us to omit the proofs of the results in Ch.\ 7 (presented in an online supplement) and focus on the discussion of statistical power and optimal design issues, which are very relevant in practice and also novel.

@@

     We agree that the core of our contribution is on the exact support recovery under dependence.  To do justice to these results, as explained above, 
     we have divided the old Chapter 4 into two new chapters.  The first part (new Ch.\ 4) highlights the role of relative stability in exact support recovery 
     under dependence. The new Ch.\ 5 more clearly presents another one of our contributions, namely the finite-sample Bayes optimality in 
     exact support recovery.  These important results were a bit obscured in the previous version of the manuscript.

     We hope that the revision has resulted in a more accessible manuscript, which at the same time more clearly highlights new ideas and results in the
     context of existing literature.

@@

     \item {\em Chapter 4-6 are relevant because they illustrate the idea of concentration of maxima for various advanced statistical topics. But the writing has several disadvantages... For example, Section 6.6.1 does not belong there and should be given in an appendix. The property of rapid variation can be introduced in an appendix...}

     Chapter 6 (now Ch.\ 7) has been thoroughly revised. 
     The proofs of phase-transition results similar to the ones in Ch.\ 3 have been omitted.  They
     will be presented in an online supplement (appearing as the Appendix section after the References).  This 
     allowed us to emphasize more clearly the novel ideas in this chapter on the parametrization of association tests and the study of their power.

@@

   \subsection{Reviewer 4 (R4)}

   We are very grateful to the reviewer for their exceptionally detailed and helpful feedback!  We appreciate the reviewer's encouraging assessment and 
   important suggestions on improving the manuscript, which have all been taken into account in the present revision.  We respond below to only some
   of the major points raised but we would be happy to provide a more detailed account.

   \begin{enumerate}
    \item {\em Most existing works assume the constant signal strength, which essentially assume that the location parameters are drawn from a two-point distribution... However, it is a bit far from realistic from my perspective because the practical case often involves a mixture of strong and weak signals. A recent paper by Li 2020 considers the generic distribution of alternative means under appropriate rescaling, and shows the surprising result that the higher criticism test no longer dominates Bonferroni’s method even in the sparse regime $\beta >3/4$. It would be more instructive if the paper can start from the more general model to provide a fuller picture.}

    \medskip
    Thank you.  We were not aware of the interesting and very recent work \cite{li2020optimality} of Li and Fithian when the first draft was prepared. We wholeheartedly agree that the set-up described by the reviewer is much more realistic.
    It is stimulating for us to learn that the Higher Criticism statistic no longer dominates the max-type Bonferonni thresholding procedure when $1/2<\beta<3/4$, as long as the signals are spread out, even if the noise terms remain Gaussian.
%    This changed our understanding about optimality of the max-statistic.  
    We now discuss and reference this recent and fascinating development in Chapters 2 and 3 where appropriate. 
%    This new development on the spread-out and heavy-tailed signals setting is parallel to the heavy-tailed noise setting that we pursued in this manuscript.

    One naturally wonders what happens, e.g., when both signals and noise terms are distributed with regularly-varying tails, and what can be said about the support recovery problems when signals are spread-out.
    Since our focus in this manuscript is weighted towards support estimation problems rather than the detection problem, we have refrained from discussing more in the direction of the more realistic setting of \cite{li2020optimality}, which would require resolving some new mathematical challenges. 
    We hope to understand this phenomenon better in the near future.

@@

    \item {\em The statistical risks for exact-approximate and approximate-exact support recovery look artificial and uninterpretable. 
    Could you provide further explanations of these two criteria?}

    We have edited the following explanation when introducing the asymmetric statistical risks:
    \begin{quote}
    $\dots$
	In applications, however, attitudes towards false discoveries and missed signals are often asymmetric.
	In the example of GWAS, where the number of candidate locations \$p\$ could be in the millions, and a class imbalance between the number of nulls and signals exists, researchers are typically interested in the marginal (location-wise) power of discovery, while exercising stringent (family-wise) false discovery control. 
	These types of asymmetric considerations, while important in applications, have not been studied theoretically.  
	For example, the GWAS application motivates the \textbackslash\{\}emph\{exact-approximate\} support recovery risk, which weighs both the family-wise error rate and the marginal power of discovery:
	$\dots$
    \end{quote}
    In fact, we believe that power calculations for GWAS is most natrually interpreted when viewed through the exact-approximate support recovery risk.

    On the other hand, we are not aware of an equally strong motivating application for the approximate-exact support recovery risk. 
    It is harder to come up with a scenario where we want to weed out a few nulls from a large number of signals, with strong type II control and evaluate marginal type I errors. 
%    However, if it had been left out, the discussion would not feel complete humanly love for symmetry.

@@

    \item {\em In practice, type-I error/FWER/FDR and type-II error/FNER/FNR are typically not equally weighted. The former is often worse than the latter. Is there any work that considers the asymmetric version like FDR plus a fraction of FNR? Does the weighted risk give a fundamentally different phase transition in some regimes?}

    There have been discussions on unequally weighted type I and type II errors. For example, the version of asymmetric risk suggested by the reviewer (i.e., $\textrm{FDR} + \lambda\textrm{FNR}$) appeared in Genovese and Wasserman \citep{genovese2002operating} Section 6, although the asymptotic limits were not discussed there.

    The asymptotic limits would not have been different for the weighted risk, so long as $\lambda$ is bounded away from zero and infinity.
    This is because $\textrm{FDR} + \lambda\textrm{FNR}$ vanishes if and only if both FDR and FNR vanish; conversely, non-vanishing FDR and FNR is equivalent to non-vanishing weighted risk.
    Therefore, the only (theoretically) interesting weighting of type I and type II errors is combining family-wise error metrics with marginal errors, as in the exact-approximate support recovery risk.

    We have added this comment on risk weighting to the manuscript.

@@

    \item {\em The uniform relative stability (URS) is type of weak dependence based on the results in Chapter 5. In FDR literature, the statistics are 
    said to be weakly dependent if 
    $$
    \frac{1}{p^2} \sum_{i=1}^n |{\rm Cor}(x_i,x_j)| = o(1),
    $$
    see e.g. Efron 2007 and Fan 2012. Is there any connection between these two types of weak dependence?}

    It can be shown that the more restrictive UDD' condition (Definition 6.2 in the new numbering) implies weak dependence as described in Fan et al \cite{fan:xu:gu:2012} (the single sum in the reviewer's comment seems to be a typo),
    $$
    \lim_{p\to\infty}\frac{1}{p^2} \sum_{i,j} |\Sigma_p(i,j)| = 0.
    $$
    Starting with the assumed permutations $l_p$ of $\{1, . . . , p\}$ in UDD', we have the equality
    $$
    \sum_{i,j} |\Sigma_p(i,j)| = \sum_{i,j} |\Sigma_p(i',j')|,
    $$
    where $i'= l_p(i)$, $j'= l_p(j)$, since permutations do not affect the sum.
    By the second assumption of a sequence $r_n\to0$ that bounds the correlations from above, we have
    $$
    \frac{1}{p^2} \sum_{i,j} |\Sigma_p(i',j')| \le \frac{1}{p^2} \sum_{i,j} r_{|i-j|} \le \frac{1}{p} \sum_{k=0}^{p-1} r_{k} \to 0.
    $$
    Therefore UDD' impies the weak dependence condition.

### 2021-04-04 reviews/response.tex

    \medskip
    We can also establish that the UDD/URS condition is no-weaker than the weak dependence condition.
    We use the same non-UDD example outlined in Example 6.1 (new numbering).
    Suppose ${\cal E} = \left(\epsilon_p(i)\right)_{i=1}^p$ is Gaussian, and is comprised of $\lfloor p^{1-\beta}\rfloor$ blocks, each of size at least $\lfloor p^\beta \rfloor$.  Let the elements within each block have correlation 1, and let the elements from different blocks be independent. 
    It follows that 
    $$
    \frac{1}{p^2} \sum_{i,j} |\Sigma_p(i,j)| \sim \frac{1}{p^2} (p^{1-\beta})^2 p^{\beta} = p^{-\beta} \to 0,
    $$
    and therefore ${\cal E}$ is weakly dependent as defined in \cite{fan:xu:gu:2012}, but not UDD/URS.

    However, it is not clear to us whether the weak dependence condition is weaker than UDD as well.
    The comparison is complicated by the fact that the definition of UDD only cares about positive correlations, while the weak dependence condition takes the sum of absolute values of the correlations.

%   \medskip
%   \noindent Indeed, the notion of {\em weak dependence} in its various forms of mixing coefficients and dependence functionals
%    has a long and fruitful history in the study of large-sample limit theorems.  
%%    We appreciate this natural question!  
%    There is a fundamental difference between the notions of weak dependence required to establish the asymptotic behavior of sums and those for maxima.     
%    As a rule, the maxima of dependent variables behave very similarly to the maxima of independent variables even under {\em severe dependence}.  This is in stark contrast with the large-sample behavior of dependent sums (averages), which have been much more extensively studied in the literature.  We have now
%    clarified and emphasized these differences in several places in the text. 
%    
%    We provide below some brief comments on the way we understand the differences between the asymptotic behaviors of sums and maxima 
%    under dependence.  This is certainly a big and important subject and the following discussion is just on the level of ideas.
%    The weak dependence condition stated by the referee appears to be tailored to the study of sums rather than maxima.  For example, a 
%    stationary (finite-variance) time-series $\{X_k,\ k\in \mathbb Z\}$ is said to be short-range dependent if
%   $$
%   \sum_{k=1}^\infty |{\rm Cov} (X_{k}, X_0) | <\infty.
%   $$
%   If the latter sum is infinite, the time series is referred to as long-range dependent. For example, consider the Gaussian case, where
%   the time series has a power-law auto-covariance ${\rm Cov}(X_{k}, X_0) \propto k^{-\gamma},\ \ k\to\infty$, for $\gamma \in (0,1)$.  In this long-range
%   dependent regime, it can be shown that, as $n\to\infty$,
%  $$
%  \Big\{ \frac{1}{n^H} \sum_{k=1}^{[nt]} (X_k -\mathbb E X_k) \Big\}_{t\ge 0} \stackrel{f.d.d.}{\longrightarrow} B_H = \{B_H(t),\ t\ge 0\},
%  $$   
%  where $B_H$ is the fractional Brownian motion process -- a Gaussian, stationary increment and  self-similar process with 
%  exponent $H = 1 - \gamma/2 \in (1/2,1)$.  This is in stark contrast with the usual Brownian motion limit which arises 
%  under the {\em weak dependence}.  The behavior of many sum-based statistics changes dramatically when the dependence switches from
%  short- to long-range.  For more details, see e.g. \cite{pipiras:taqqu:2017} and the references therein.
%  
%  Shockingly, when considering even most heavily dependent (say long-range dependent) Gaussian
%   stationary time series $\{X_k\}$, the limit behavior of the maxima
%  is no different than in the iid case.  Indeed, the Berman condition (cf \cite{berman1964limit,leadbetter2012extremes})
%  $$
%  {\rm Cov}(X_k,X_0) = o \Big(\frac{1}{\log k}\Big),\ \ \mbox{ as }k\to\infty,
%  $$
%  guarantees in this setting that, as $n\to\infty$,
%  \begin{equation}\label{e:Gumbel}
%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k - b_n \stackrel{d}{\longrightarrow} Z \sim {\rm Gumbel},
%  \end{equation}
%  where $a_n$ and $b_n$ are {\em the same} scaling and shift sequences as in the case of iid data.  That is, if $X_k^*$ are iid with the same marginal 
%  distribution as the $X_k$'s, then
%  $$
%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k^* - b_n \stackrel{d}{\longrightarrow} Z,
%  $$
%  where the normalizing constants $a_n$ and $b_n$ as well as the limit $Z$ are the same as in \eqref{e:Gumbel}.
%  
%  In particular, the Berman condition holds for most Gaussian long-range dependent models!  Thus, even when the traditional notions of weak dependence for
%  sums no longer hold, the dependence is weak enough for the maxima to behave as in the iid setting.  Please note that in our monograph we need an even weaker notion of dependence since we need only have relative stability, i.e., 
%  \begin{equation}\label{e:RS}
%  \frac{1}{a_n} \max_{k=1,\cdots,n} X_k \stackrel{\P}{\longrightarrow} 1,
%  \end{equation}
%  as $n\to\infty$.  As shown in the seminal work of Berman \cite{berman1964limit} and in a more general situation for triangular arrays in our 
%  Chapter 6), for the latter convergence \eqref{e:RS} to hold one merely needs the auto-covariance to vanish, i.e., 
%  $$
%  {\rm Cov}(X_k,X_0) = o(1),\ \ \ \mbox{ as }k\to\infty.
%  $$
%  We find this to be an important and perhaps somewhat overlooked universality phenomenon showing that maxima of Gaussians 
%  (and perhaps much more broad classes of light-tailed arrays) continue to concentrate under drastically stronger dependence than we are 
%  accustomed to deal with in the case of sums/averages.
%

@@

    \item {\em This is another line of work that studies the strong dependence structure where the covariance matrix has a factor structure (eg. Fan 2012). For instance, this includes the equi-correlated case. Are you aware of any results under strong dependence in your context?}

    We thank the reviewer for pointing to the interesting methodological work of Fan, Xu and Gu \cite{fan:xu:gu:2012}, which aimed to estimate false discovery proportions for heavily dependent observations. 
    We are not aware of works that discuss optimality or feasibility of support recovery (i.e., multiple testing) problems under such dependence conditions.
    The results in our text in their current form do easily extend to that of Fan et al., since even the remainder term $K_i$'s in the factor model can be more heavily dependent than under the UDD/URS condition, as discussed in the response to the previous question.
    Nevertheless, Fan et al provides a glimpse into how heavy dependence (e.g., the equi-correlated case) may be handled, and how theoretical analysis may be carried out. We do hope to develop general theory that applies to the more setting.
%   It can be seen that the {\em weak dependence} condition in their Definition 1, implies our UDD condition (for a correlation matrix).  
%   Therefore, the Gaussian error arrays of the $K_i$-variables in Relation (10) in the latter reference, are URS (uniformly relatively stable).  
%   This suggests that the PFA methodology in \cite{fan:xu:gu:2012} can perhaps be extended to apply to the exact support recovery problem.  
%   That is, one can project on the orthogonal complement of the space spanned by the top$-k$ eigenvectors of the error-covariance.  Then, perhaps 
%   under standard in-coherence conditions, between the  signal and the covariance, the simple Bonferonni thresholding estimator is optimal for exact 
%   support recovery.  
%   We are not aware of many more examples, but hope that the developed general theory applies in many more setting.

@@

    \item {\em Proposition 4.3 still requires $f_a$ to be MLR, right? If so, please state it.}

    Thank you for the sharp observation.  The previous presentation was not sufficiently clear.  We have now devoted the new Ch.\ 5 to the
    finite-sample Bayes optimality (and minimax optimality) to better present these topics.  
    The former Proposition 4.3 appears now as Theorem 5.2.  The MLR property on $f_a$
    is no longer necessary.  This is because the {\em likelihood ratio theresholding} estimator is defined in such a way (in terms of the likelihood) that
    the desired monotonicity property is guaranteed.  The MLR property was essential in Theorem 5.1 since there we deal with thresholding (as opposed to
    likelihood thresholding). The MLR property basically ensures that in the setting of Theorem 5.1, the simple thresholding estimators are in fact of
    {\em likelihood thresholding} type.  We realize that Theorem 5.2 is a bit too theoretical (i.e., not directly useful in practice since we don't have the 
    likelihood) but it provides some insights on
    the general Bayes (sub)optimal support estimation procedures.

    \item  {\em Fig 3.2 shows that the exact-approximate support recovery is strictly easier to achieve than the approximate-exact support recovery. Do you have intuition on it?}

    To provide an intuition, consider the distances between the decision boundaries and the means of the null and signal part of the observations, respectively.
    Controlling the FWER requires setting the decision boundaries approximately 
    \begin{equation} \label{FWER}
    \sqrt{2\log{p}}
    \end{equation}
    away from zero (mean of nulls), as is well-known in the Bonferroni adjustment.

    Controlly FDR, on the other hand, depends on the number of signals present.
    When there are fewer signals, a FDR-controlling procedure has to be more conservative -- when the number of true signals is small, the number of false discoveries reported along with them has to reduce as well.
    Consequently, the decision boundary has to be further away from zero as $\beta\to1$.
    Quantitatively, this distance varies with $\beta$ approximately as
    \begin{equation} \label{FDR}
    \sqrt{2\beta\log{p}},
    \end{equation}
    with sparser problems requiring a larger separation. 
    Notice that the distance required for FDR control in an extremely sparse problem ($\beta\to1$) is no different from that of FWER control.
    For very dense problems ($\beta\to0$), the distance vanishes on the Bonferroni scale.

    Similar to FWER, controlling the family-wise non-discovery rate (FWNR) requires this boundary to be approximately
    \begin{equation} \label{FWNR}
    \sqrt{2\log{(p^{1-\beta})}} = \sqrt{2(1-\beta)\log{p}}
    \end{equation}
    away from the mean of the signals.

    Finally, controlling false non-discovery ratio (FNR) is similar to FDR control, except the class imbalance reverses -- the null part greatly out numbers the signals.
    Therefore the separation between the decision boundary and the mean of signals can afford to be small.
    So small that it vanishes on the Bonferroni scale:
    \begin{equation} \label{FNR}
    o\left(\sqrt{2\log{p}}\right).
    \end{equation}

    Informally, mixing and matching the two distances from nulls \eqref{FWER} and \eqref{FDR} with the two distances from signals \eqref{FWNR} and \eqref{FNR} gives rise to the four boundaries we derive in this text. 
    The fact that exact-approximate support recovery is strictly easier than approximate-exact support recovery is a consequence of \eqref{FWER} + \eqref{FNR} $\le$ \eqref{FDR} + \eqref{FWNR}.
    But it is ultimately a consequence of the assumption on signal sparsity. That is, when there are more nulls than signals, the separation between the signals and the nulls has to be larger for simultaneous FDR and FWNR control.
    % when the number of nulls is much larger than the number of signals $p\gg p^{1-\beta}$.

### 2021-04-04 3.phase_transitions/3.BH_monotonicity.tex
many changes... Chapter 4 intro WIP

We make a connection between power of the \ac{BH} procedure and the stochastic ordering of distributions under the alternative.
This result, though natural, seems new.

@@

\begin{proof}[Proof of Lemma \ref{lemma:monotonicity-BH-procedure}]
We first re-express the BH procedure in a different form.
Recall that on observing $x(i)$, $i\in\{1,\ldots,p\}$, the BH procedure is the thresholding procedure with threshold set at $x_{[i^*]}$, where $i^* := \max\{i\,|\,\overline{F_0}(x_{[i]})\le \alpha i/p\}$, and $x_{[1]}\ge\ldots\ge x_{[p]}$ are the order statistics.

>>>>

As promised in the previous section, we make a connection between power of the \ac{BH} procedure and the stochastic ordering of distributions under the alternative.
This natural result seems new.

@@

\begin{proof}[Lemma \ref{lemma:monotonicity-BH-procedure}]
We first re-express the BH procedure in a different form.
Recall that on observing $x(i)$, $i\in\{1,\ldots,p\}$, the BH procedure is the thresholding procedure with threshold set at $x_{[i^*]}$, where $i^* := \max\{i\,|\,\overline{F_0}(x_{[i]})\le \alpha i/p\}$, and $x_{[1]}\ge\ldots\ge x_{[p]}$ are the order statistics.
